Implementation of a Fuzzy Rule-Based Classifier using Genetic Algorithms

### 2017-12-15 Article/article.tex
Added more figures, some minor fixes, changed a bit some paragraphs, and added a foreword

\documentclass[a4paper,12pt]{article}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{
	urlcolor=red,
	linkcolor=red,
	colorlinks=red,
}

\begin{document}
\title{Implementation of a Fuzzy Rule-Based Classifier using Genetic Algorithms}
\author{Rashed,David,Joseph}
\maketitle
%\pagestyle{headings}

@@

Fuzzy set is defined by Membership function

Fuzzy variable/Linguistic concepts

A fuzzy system goes through three processes : fuzzification, inference, and finally defuzzification. Each of these process will be described.

\subsection{Fuzzification}

Fuzzification is the first step of a fuzzy system. It takes crisp input values and turns them into fuzzy values through a membership functions.
For our classifier, we have designed 3 linguistic variables for each of the parameters. In total, we have 12 membership functions.
The three linguistics variables are SMALL, MEDIUM and LARGE. We decided to have the same functions for each of the parameters.

(PLOT OF THE THREE FUNCTIONS??)

\subsection{Inference system}

\subsection{Defuzzification}

A fuzzy rule-based system has two components: the Knowledge Base and the Inference System.

Knowledge Base : storing the available knowledge in the form of fuzzy rules
Inference system : applying a fuzzy reasoning method on the inputs and the KB rules to give a system output.

The knowledge base is usually obtained from expert knowledge, but also by machine learning since the field emerged in the 80s.

>Data base:
Granularity (nb of ling terms/labels)/ var
Membership functions associated to the labels
>Rule Base: fuzzy rule composition

KB is composed of RB and DB
RB: Rule set, DB: Membership funct

input>fuzzification interface>inference mechanism (applying RB \& DB)>Defuzzification Interface> output

Inference System is set up by choosing the fuzzy operator for each component (conjunction, implication, defuzzifier, etc...)

\subsection{Classification model for fuzzy rules}
For each of these attributes $x_{i}(i=1\cdots n)$ there are three fuzzy sets that are denoted A(i,S), A(i,M), A(i,L), respectively for Small, Medium and Large.
Let's define \textbf{p} as the mapping function from $\{1\cdots s(s\leq4)\}$ to $\{1\cdots4\}$, with $\forall x\neq y, p(x)\neq p(y)$. We use this function to express that not all parameters are needed in a rule.
Thus we can generalize rules as follows :

@@

@@

Genetic Algorithms can be used for various parts of a fuzzy system:

Tuning the membership function
Rule learning
Rule selection
Learning of Knowledge Base
Inference parameters
Etc... (see \url{http://sci2s.ugr.es/sites/default/files/files/TematicWebSites/GeneticFuzzySystems/FUZZ-IEEE09_Tutorial_EMOFRBSs-Ishibuchi-Alcala.pdf})

@@

\subsection{The fitness function}

According to the law of the fittest, the best individuals have more of a chance of breeding and transmitting their genes. But what does it mean for an individual to be fit?\\
For this work, we define the fitness function as the accuracy of prediction of an individual given a test dataset.

\section{Implementation}

Optimization : cache individual rule fitnesses\\
Set of rules : may be rules that are incorrect

\section{Results and Conclusion}

@@

@@

\[\mu_A=
min
\begin{pmatrix}
max(A(p(1),j),\forall j \in D(1))\\
\vdots \\
max(A(p(s),j),\forall j \in D(s))
\end{pmatrix}
    \]
\textbf{Example:}\\
\\
Lets take our example rule:
\begin{center}
If Sepal Length is Small AND Sepal Width is Medium OR Big AND Petal Width is Small OR Medium OR Big
\end{center}
And a data instance (normalized): $x_1=0.97,x_2=0.86,x_3=0.97,x_4=0.88$.\\
\[
\begin{split}
\mu_A &= min
\begin{pmatrix}
max(\mu_S(0.97))\\
max(\mu_M(0.86),\mu_B(0.86))\\
max(\mu_S(0.88),\mu_M(0.88),\mu_B(0.88))
\end{pmatrix}\\
&= min
\begin{pmatrix}
max(0)\\
max(0.28,0.72)\\
max(0,0.24,0.76)
\end{pmatrix}\\
&= min(0,0.72,0.76) = 0
\end{split}
\]
\\
\begin{center} \rule[1ex]{.5\textwidth}{.5pt} \end{center}
\newpage

@@

We now want to get the predicted confidence of classes for an instance.\\
$\vec{Conf}$ gives us the fittest class for each rule, and $\vec{\mu_A}$ its confidence given an instance of data. \\
There are several ways to compute the class predicted using these vectors.
\\
\\
\textbf{Simple method:}
\\
For each class, we take the average of $\mu_A$ for every rule that has that class as the highest truth degree:
\[
\text{Predicted Classes Confidence: }
\begin{pmatrix}
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_1\\
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_2\\
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_3
\end{pmatrix}
\]
Here, the class predicted will simply be the maximum average.

@@

The accuracy gives us the percentage of well predicted instances of our classification on a test data. We can use only this score as a fitness function.\\
It seems that using the training data to define the truth degree, then applying the simple method is already a good way to classify.\\
When taking the average of the average accuracy of 20 populations of 20 randomly generated individuals, we have a 0.77 accuracy.\\
And when taking the average accuracy of the fittest individual of 20 random populations, we get a 0.96 accuracy.\\
Decision Tree Classifier is a similar method with crisp rules. The accuracy of that method is 0.92 on the same dataset.\\
However, the accuracy score is not our only concern : we would like to have the fewest rules as possible, as we want to produce a clear and simple rule system if one exists. So we have to compute a fitness function combining both the accuracy score and the complexity of the rule set.
This is where we decided to change our fitness function in this way:

@@

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{ {img/} }

\hypersetup{
	urlcolor=red,
	linkcolor=red,
	colorlinks=red,
}

\begin{document}
\title{Implementation of a Fuzzy Rule-Based Classifier using Genetic Algorithms}
\author{Mona Rashed,Quentin David,Joseph Yaconelli}
\date{December 2017}
\maketitle
%\pagestyle{headings}

\section{Foreword}

Our code can be download in this github link:
\url{https://github.com/Apoptoz/FL_Classifier}
To launch the program, simply type \textit{python3 GAA.py} in a terminal.
You can tune the parameters in the file GAA.py and classifier.py.\\
\\
We shared the work this way:\\
Rashed: \\
Joseph: \\
Quentin: \\

@@

\begin{center}
\includegraphics[scale=0.5]{fuzzysystem}
\end{center}

Fuzzification is the first step of a fuzzy system. It takes crisp input values and turns them into fuzzy values through a membership functions.
For our classifier, we have designed 3 linguistic variables for each of the parameters. In total, we have 12 membership functions.
The three linguistics variables are SMALL, MEDIUM and LARGE. We decided to have the same functions for each of the parameters.
All the parameters are normalized so we get for all a value between 0 and 1.

\begin{center}
\includegraphics[scale=0.5]{fuzzymembership}
\end{center}

The inference is the process of getting an ouput given an output. For a classification task, the output will be the predicted class.
This process is described in the Fitness function section.

Finally, the defuzzification is the part where we map our output into a quantifiable crisp value. For a classification task, the defuzzification consist in taking the class with have the most average accuracy. Again, this step is explained in the fitness function section.

\section{Confidence degree of a rule}
For each of these attributes $x_{i}(i=1\cdots n)$ there are three fuzzy sets that are denoted A(i,S), A(i,M), A(i,L), respectively for Small, Medium and Large.
Let's define \textbf{p} as the mapping function from $\{1\cdots s(s\leq4)\}$ to $\{1\cdots4\}$, with $\forall x\neq y, p(x)\neq p(y)$. We use this function to express that not all parameters are needed in a rule.
Thus we can generalize rules as follows :

@@

Genetic Algorithm is a heuristic search algorithm based on the law of evolution to reach for an optimal solution within a problem space. GA are good for multi-dimensional problems.

\begin{center}
\includegraphics[scale=0.5]{genealgo}
\end{center}

@@

Genetic Algorithms can be used for various parts of a fuzzy system:\\
\\
Tuning the membership function\\
Rule learning\\
Rule selection\\
Learning of Knowledge Base\\
Inference parameters\\
Etc... (see \url{http://sci2s.ugr.es/sites/default/files/files/TematicWebSites/GeneticFuzzySystems/FUZZ-IEEE09_Tutorial_EMOFRBSs-Ishibuchi-Alcala.pdf})

\begin{center}
Genetic algorithm to learn a fuzzy rulebase
\includegraphics[scale=0.5]{genefuzzy}
\end{center}

@@

@@

\begin{center}
\includegraphics[scale=0.3]{fitnessfunct}
\end{center}

@@

\[\mu_A=
min
\begin{pmatrix}
max(A(p(1),j),\forall j \in D(1))\\
\vdots \\
max(A(p(s),j),\forall j \in D(s))
\end{pmatrix}
    \]
\textbf{Example:}\\
\\
Lets take our example rule:
\begin{center}
If Sepal Length is Small AND Sepal Width is Medium OR Big AND Petal Width is Small OR Medium OR Big
\end{center}
And a data instance (normalized): $x_1=0.97,x_2=0.86,x_3=0.97,x_4=0.88$.\\
\[
\begin{split}
\mu_A &= min
\begin{pmatrix}
max(\mu_S(0.97))\\
max(\mu_M(0.86),\mu_B(0.86))\\
max(\mu_S(0.88),\mu_M(0.88),\mu_B(0.88))
\end{pmatrix}\\
&= min
\begin{pmatrix}
max(0)\\
max(0.28,0.72)\\
max(0,0.24,0.76)
\end{pmatrix}\\
&= min(0,0.72,0.76) = 0
\end{split}
\]
\\

@@

We now want to get the predicted confidence of classes for an instance.\\
$\vec{Conf}$ gives us the fittest class for each rule, and $\vec{\mu_A}$ its confidence given an instance of data.
\[
\text{Predicted Classes Confidence: }
\begin{pmatrix}
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_1\\
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_2\\
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_3
\end{pmatrix}
\]
Here, the class predicted will simply be the maximum average.

@@

The accuracy gives us the percentage of well predicted instances of our classification on a test data. We can use only this score as a fitness function.
However, the accuracy score is not our only concern : we would like to have the fewest rules as possible, as we want to produce a clear and simple rule system if one exists. So we have to compute a fitness function combining both the accuracy score and the complexity of the rule set.
This is where we decided to change our fitness function in this way:

@@

\begin{center}
\includegraphics[scale=0.5]{accresult}
\end{center}
